Efficient Development Framework with mruby for Embedded Systems

### 2016-06-03 CPSNA2016/paper.tex
update

%
% File: thesis.tex
% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
%
\input{dummy/dummy.tex}
\documentclass[conference]{IEEEtran}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\small\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    %lineskip=-0.5ex%
}

\title{Bluetooth Loader for mruby Bytecode \\ in Multiple Virtual Machine Environment}
\author{\IEEEauthorblockN{Takuro Yamamoto}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
\and\IEEEauthorblockN{Hiroshi Oyama}\IEEEauthorblockA{OKUMA Corporation}
\and\IEEEauthorblockN{Takuya Azumi}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
}

\begin{document}
\maketitle
\begin{abstract}
Recently, the productivity of embedded systems has become problematic due to their increasing complexity and scale.
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs mruby (i.e., lightweight Ruby) and supports component-based development, has been proposed.
In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
Moreover, while the framework supports multiple virtual machines (VMs), developers must be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs concurrently or in parallel.
To improve development efficiency, we propose a Bluetooth loader for mruby bytecode as an extension of mruby on TECS.
The loader executes two mruby bytecodes, i.e., the mruby application bytecode and mruby library bytecode.
The mruby application bytecode is modified frequently and sent from a host to a target device by the developers, while the mruby library bytecode is modified infrequently and preserved beforehand on a storage/ROM device during the first compilation.
In addition, multiple mruby programs can run cooperatively in the proposed framework.
Compared to mruby on TECS, the RiteVM scheduler simplifies multitasking.
Synchronization of initializing multiple tasks is also implemented using an Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}

\section{Introduction}
Currently, embedded systems, e.g., Internet of Things applications, must demonstrate high quality and high performance.
This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.

Complex and large-scale software systems can be developed efficiently by using component-based techniques \cite{par:Crnkovic}, \cite{par:CBD}.
Component-Based Development (CBD) is a design technique that can be applied to reusable software development.
% Complex and large scale software systems can be developed efficiently using component-based techniques.
% That is because software componentization provides high-reusability.
% Verification of component-based systems has been extensively researched \cite{par:Blaming}, \cite{par:Verification}.
Individual component diagrams enable the visualization of an entire system.
%It also visualize the entire system due to component diagrams, and makes a system flexible in extensions and specification changes.
In addition, component-based systems are flexible with regard to extensibility and specification changes.
The TOPPERS embedded component system (TECS) \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} are typical CBD tools for embedded systems.

In addition, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to software development.
Currently, most software are programmed in C language.
However, development in C language results in large code size, incurs high costs, and requires significant development time.
In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because it is relatively easy to reuse scripts. 
% script languages have high-productivity from their usability.
% Ruby, JavaScript, Perl, Python, and Lua are well-known as representative script languages.

@@

To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}.
This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, \cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}, \cite{url:TOPPERS}.
% mruby on TECS supports to effectively run mruby script language on embedded systems.
% mruby on TECS also makes execution time 100 times faster than that of mruby.

%This paper proposes two additional features of mruby on TECS, Bluetooth loader for mruby bytecode and RiteVM scheduler.
Even though execution times of mruby on TECS are 100 times faster than those of mruby, it is not particularly efficient, at present, and imposes a heavy burden on developers.
Moreover, mruby on TECS only supports a storage/ROM device for loading mruby programs.
Consequently, if mruby programs are modified, a secure digital (SD) card must be inserted and removed repeatedly or ROM must be rewritten; moreover, developers need to restart real-time operating systems (RTOSs) on the target device.
In addition, although mruby on TECS can support multiple virtual machines (multi-VMs), executing multiple tasks requires the developers to call the OS function.

This paper proposes an extended framework of mruby on TECS that comprises a Bluetooth loader for mruby bytecode and a RiteVM scheduler for fairly executing mruby programs.
To improve development efficiency, in the proposed framework, developers need to implement the platform on a storage device only once at the beginning and can transfer mruby application programs from a host to a target device using the Bluetooth loader.
Note that RiteVM is the Ruby VM specifically designed for embedded systems.
The RiteVM scheduler manages the execution of multiple RiteVMs and allows developers to program multitasking more easily than the current version of mruby on TECS.

{\bf Contributions}: The proposed framework provides the following contributions:
\begin{enumerate}
\item {\bf Improved software development efficiency.}
Developers do not need to rewrite a storage/ROM device and restart an RTOS.
The Bluetooth loader supports continuous loading, which reduces Bluetooth set-up time (i.e., pairing).
\item {\bf Execution of multiple mruby programs concurrently or in parallel.}
Developers can implement multiple tasks without RTOS knowledge because the RiteVM scheduler switches tasks cyclically.
\item {\bf Synchronized execution of multiple RiteVM tasks.}
The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
\item {\bf Benefits of CBD:}
The paper focuses on the benefits of CBD and provides specific examples.
\end{enumerate}

{\bf Organization}: The reminder of this paper is organized as follows.
Section \ref{sec:Background} introduces the basic technologies, i.e., mruby, TECS, and mruby on TECS.
Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
Section \ref{sec:Evaluation} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/proposed.eps}
    \caption{System model of the proposed framework}
    \label{fig:proposed}
\end{figure}

\section{Background}
\label{sec:Background}
Figure \ref{fig:proposed} shows the system model of the proposed framework.
Note that the RiteVMs and the mruby library are assumed to be prepared in advance.
Bytecodes are transferred from the host to the target device via Bluetooth, and each RiteVM is allocated a bytecode.
Bytecodes transferred from the host via Bluetooth can run in multitask.

\subsection{mruby}
\label{sec:mruby}
mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
Ruby is an object-oriented scripting language \cite{url:Ruby} with classes and methods, exceptions, and garbage collection functions.
It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.

mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/mruby.eps}
    \caption{mruby/RiteVM mechanism}
    \label{fig:mruby}
\end{figure}

\subsection{TECS}
\label{sec:TECS}
TECS is a component system suitable for embedded systems.
TECS can increase productivity and reduce development costs due to improved reusability of software components.
TECS also provides component diagrams, which help developers visualize the overall structure of a system.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
    \caption{Component Diagram}
    \label{fig:component}
\end{figure}

\subsubsection{Component Model}
Figure \ref{fig:component} shows a component diagram.
A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
A {\it signature} is the interface definition of a {\it cell}.
The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and internal variables of a {\it cell}.

\begin{description}
    \item[{\bf Signature Description}]\mbox{}\\
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor {
    int32_t getCounts( void );
    ER resetCounts( void );
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
    ER rotate( [in] int degrees, [in] uint32_t speed_abs,
              [in] bool_t blocking );
    void initializePort( [in]int32_t type );
};
\end{lstlisting}
\caption{Signature Description}
\label{signature}
\end{figure}
    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr {
        int32_t port;
    };
    var {
        int32_t currentSpeed = 0;
    };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}
    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate and connect {\it cell}s.
        Figure \ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
        In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\caption{Build Description}
\label{build}
\end{figure}

\subsection{mruby on TECS}
\label{sec:mruby on TECS}
% mruby on TECS is a component-based framework for running script language.
% This framework uses two technologies, mruby and TECS.

\subsubsection{System Model}
The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
% The mruby-TECS bridge is described in more detail bellow.

In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{par:ASP}, \cite{url:ASP}.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
\caption{System model of existing mruby on TECS}
\label{fig:mrubyontecs}
\end{figure}

\subsubsection{mruby-TECS Bridge}
There is a significant difference between the execution times of mruby and C language codes.
According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
Thus, it is difficult to use mruby exclusively.

Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
The left side of BridgeMotor belongs to the mruby program.
The right side of BridgeMotor belongs to TECS component.
\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
\caption{mruby-TECS bridge}
\label{fig:mruby_TECS_bridge}
\end{figure}

\section{Design and Implementation}
\label{sec:Design and Implementation}
Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
Each mruby application bytecode transferred from the host to the target device is received by the loader in the RiteVM.
The RiteVM reads the transferred bytecode and executes it with libraries.
The mruby applications run simultaneously due to synchronized processing.
The RiteVM scheduler switches RiteVM tasks because multiple tasks can run concurrently.
The following subsection explains these functionalities.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/system_model.eps}
\caption{Detailed system model of the proposed framework}
\label{fig:system_model}
\end{figure}

\subsection{Bluetooth Loader for mruby Bytecode}
\label{sec:Bluetooth loader for mruby bytecode}
This section describes the proposed additional functionality of mruby on TECS, i.e., the Bluetooth loader, for mruby bytecode.\footnote{
The Bluetooth loader is intended to improve development efficiency; therefore, software developers should use it during the development phase.
Note that the complete software should be compiled and linked on the storage/ROM device beforehand.
}
In the current system, the platform including mruby bytecodes is saved on a storage/ROM device.
Developers must rewrite the storage/ROM device every time the programs are modified.
In addition, the RTOS on the target device needs to be restarted.
The repetition hinders development efficiency.
The Bluetooth loader for mruby bytecode decreases developer burden because developers only have to connect the storage/ROM device and start the RTOS once.

@@

In the proposed framework, a platform that includes RiteVMs and an mruby library is first compiled and copied to the storage/ROM device.
On the host, the mruby application programs (.rb files) are edited and compiled to bytecodes (.mrb files) by an mruby compiler.
The generated bytecodes are transferred from the host to the target device via Bluetooth.
This saves time since Bluetooth pairing can be avoided because the loader can load the bytecode continuously.

>>>>

%
% File: paper.tex
% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
%
\input{dummy/dummy.tex}
\documentclass[conference]{IEEEtran/IEEEtran}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\footnotesize\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

% \title{Efficient Devlopment Framework applied Scripting Language for Embedded Systems}
\title{Efficient Development Framework with mruby for Embedded Systems}
\author{\IEEEauthorblockN{Takuro Yamamoto}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
\and\IEEEauthorblockN{Hiroshi Oyama}\IEEEauthorblockA{OKUMA Corporation}
\and\IEEEauthorblockN{Takuya Azumi}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
}

\begin{document}
\maketitle
\begin{abstract}
Recently, the productivity of embedded systems has become problematic due to their increasing complexity and scale.
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs scripting language (i.e., mruby) and supports component-based development, has been proposed.
This paper proposes an extended framework of mruby on TECS that improve development efficiency more than the current version.
In the proposed framework, a Bluetooth loader which receives a transferred mruby bytecode from a host, and a RiteVM scheduler which simplifies multitasking are implemented.
% In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
% Moreover, while the framework supports multiple virtual machines, developers must be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs concurrently or in parallel.
% To improve development efficiency, we propose a Bluetooth loader for mruby bytecode as an extension of mruby on TECS.
% The loader executes two mruby bytecodes, i.e., the mruby application bytecode and mruby library bytecode.
% The mruby application bytecode is modified frequently and sent from a host to a target device by the developers, while the mruby library bytecode is modified infrequently and preserved beforehand on a storage/ROM device during the first compilation.
% In addition, multiple mruby programs can run cooperatively in the proposed framework.
% Compared to mruby on TECS, the RiteVM scheduler simplifies multitasking.
% Synchronization of initializing multiple tasks is also implemented using an Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}

\section{Introduction}
Currently, embedded systems must demonstrate high quality and high performance.
This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.

Complex and large-scale software systems can be developed efficiently by using component-based techniques \cite{par:Crnkovic}.
Component-Based Development (CBD) is a design technique that can be applied to reusable software development.
% Complex and large scale software systems can be developed efficiently using component-based techniques.
% That is because software componentization provides high-reusability.
% Verification of component-based systems has been extensively researched \cite{par:Blaming}, \cite{par:Verification}.
Individual component diagrams enable the visualization of an entire system.
%It also visualize the entire system due to component diagrams, and makes a system flexible in extensions and specification changes.
In addition, component-based systems are flexible with regard to extensibility and specification changes.
TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} are typical CBD tools for embedded systems.

In addition, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to software development.
Currently, most software are programmed in C language.
However, development in C language results in large code size, incurs high costs, and requires significant development time.
In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because of their usability. 
% script languages have high-productivity from their usability.
% Ruby, JavaScript, Perl, Python, and Lua are well-known as representative script languages.

@@

To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}.
This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}.
% mruby on TECS supports to effectively run mruby script language on embedded systems.
% mruby on TECS also makes execution time 100 times faster than that of mruby.

%This paper proposes two additional features of mruby on TECS, Bluetooth loader for mruby bytecode and RiteVM scheduler.
Even though execution times of mruby on TECS are 100 times faster than those of mruby, it is not particularly efficient, at present, and imposes a heavy burden on developers.
mruby on TECS only supports a storage/ROM device for loading mruby programs.
Consequently, if mruby programs are modified, an SD card must be inserted and removed repeatedly or ROM must be rewritten; moreover, developers need to restart an RTOS on the target device.
In addition, although mruby on TECS can support multi-VM, executing multiple tasks requires the developers to call the OS function.

This paper proposes an extended framework of mruby on TECS that comprises a Bluetooth loader for mruby bytecode and a RiteVM scheduler for fairly executing mruby programs.
To improve development efficiency, in the proposed framework, developers need to implement the platform on a storage device only once at the beginning and can transfer mruby application programs from a host to a target device using the Bluetooth loader.
% Note that RiteVM is the Ruby VM specifically designed for embedded systems.
The RiteVM scheduler manages the execution of multiple RiteVMs (i.e., VMs designed for mruby) and allows developers to program multitasking more easily than the current version of mruby on TECS.

{\bf Contributions}: The proposed framework provides the following contributions:
\begin{enumerate}
    \vspace{-2mm}
\item {\bf Improved software development efficiency.}
Developers do not need to rewrite a storage/ROM device and restart an RTOS.
% The Bluetooth loader supports continuous loading, which reduces Bluetooth set-up time (i.e., pairing).
\item {\bf Execution of multiple mruby programs concurrently or in parallel.}
Developers can implement multiple tasks without RTOS knowledge because the RiteVM scheduler switches tasks cyclically.
\item {\bf Synchronized execution of multiple RiteVM tasks.}
The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
\item {\bf Benefits of CBD:}
The paper focuses on the benefits of CBD and provides specific examples.
    \vspace{-2mm}
\end{enumerate}

{\bf Organization}: The reminder of this paper is organized as follows.
Section \ref{sec:System Model} introduces the system model, and Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
Section \ref{sec:Evaluation} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.6cm,clip]{figure/proposed.eps}
%     \caption{System model of the proposed framework}
%     \label{fig:proposed}
% \end{figure}

% \section{Background}
% \label{sec:Background}
% Figure \ref{fig:proposed} shows the system model of the proposed framework.
% Note that the RiteVMs and the mruby library are assumed to be prepared in advance.
% Bytecodes are transferred from the host to the target device via Bluetooth, and each RiteVM is allocated a bytecode.
% Bytecodes transferred from the host via Bluetooth can run in multitask.
%
% \subsection{mruby}
% \label{sec:mruby}
% mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
% Ruby is an object-oriented scripting language \cite{url:Ruby} with classes and methods, exceptions, and garbage collection functions.
% It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
% Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.
%
% mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
% In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
% The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
% The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.6cm,clip]{figure/mruby.eps}
%     \caption{mruby/RiteVM mechanism}
%     \label{fig:mruby}
% \end{figure}
%
% \subsection{TECS}
% \label{sec:TECS}
% TECS is a component system suitable for embedded systems.
% TECS can increase productivity and reduce development costs due to improved reusability of software components.
% TECS also provides component diagrams, which help developers visualize the overall structure of a system.
%
% In TECS, component deployment and composition are performed statically.
% Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
% TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.
%
% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
%     \caption{Component Diagram}
%     \label{fig:component}
% \end{figure}
%
% \subsubsection{Component Model}
% Figure \ref{fig:component} shows a component diagram.
% A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and variables.
% An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
% A {\it cell} has one or more {\it entry} ports and {\it call} ports.
% {\it Cell} functions are implemented in C.
%
% The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
% A {\it signature} is the interface definition of a {\it cell}.
% The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
% Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and variables of a {\it cell}.
%
%
% \subsubsection{Component Description}
% In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
% % TECS code is written in CDL (component description language) file.
% These components are described as follows.
%
% \begin{description}
%     \item[{\bf Signature Description}]\mbox{}\\
%         The {\it signature} defines a {\it cell} interface.
%         The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
%         In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
% \begin{figure}[t]
% \centering
% \begin{lstlisting}
% signature sMotor {
%     int32_t getCounts( void );
%     ER resetCounts( void );
%     ER setPower( [in]int power );
%     ER stop( [in] bool_t brake );
%     ER rotate( [in] int degrees, [in] uint32_t speed_abs,
%               [in] bool_t blocking );
%     void initializePort( [in]int32_t type );
% };
% \end{lstlisting}
% \caption{Signature Description}
% \label{signature}
% \end{figure}
%     \item[{\bf Celltype Description}]\mbox{}\\
%         The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
%         A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
%         To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
%         {\it Call} ports are defined similarly.
%         Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
% \begin{figure}[t]
% \centering
% \begin{lstlisting}
% celltype tCaller {
%     call sMotor cMotor;
% };
% celltype tMotor {
%     entry sMotor eMotor;
%     attr { int32_t port; };
%     var { int32_t currentSpeed = 0; };
% };
% \end{lstlisting}
% \caption{Celltype Description}
% \label{celltype}
% \end{figure}
%     \item[{\bf Build Description}]\mbox{}\\
%         The build description is used to instantiate and connect {\it cell}s.
%         Figure \ref{build} shows an example of a build description.
%         A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
%         To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
%         In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
%         {\it C\_EXP} calls macros defined in C files.
%
% \begin{figure}[t]
% \centering
% \begin{lstlisting}
% cell tMotor Motor {
%     port = C_EXP("PORT_A");
% };
% cell tCaller Caller {
%     cMotor = Motor.eMotor;
% };
% \end{lstlisting}
% \caption{Build Description}
% \label{build}
% \end{figure}
%
% \end{description}
%
% \subsection{mruby on TECS}
% \label{sec:mruby on TECS}
% % mruby on TECS is a component-based framework for running script language.
% % This framework uses two technologies, mruby and TECS.
%
% \subsubsection{System Model}
% The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
% Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
% TECS components support various embedded drivers such as motor and sensor drivers.
%
% An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
% The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
% % The mruby-TECS bridge is described in more detail bellow.
%
% In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
% However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{par:ASP}, \cite{url:ASP}.
%
% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
% \caption{System model of existing mruby on TECS}
% \label{fig:mrubyontecs}
% \end{figure}
%
% \subsubsection{mruby-TECS Bridge}
% There is a significant difference between the execution times of mruby and C language codes.
% According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
% Thus, it is difficult to use mruby exclusively.
%
% Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
% However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
% % On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.
%
% Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
% The left side of BridgeMotor belongs to the mruby program.
% The right side of BridgeMotor belongs to TECS component.
% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
% \caption{mruby-TECS bridge}
% \label{fig:mruby_TECS_bridge}
% \end{figure}
%
% The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
%
% The generated mruby-TECS bridge supports registration of classes and methods for mruby.
% Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
% Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
%

\section{System Model}
\label{sec:System Model}
The proposed framework is an extended framework of mruby on TECS, and utilizes mruby and TECS.
These basic technologies are described in appendix of this paper.

Figure \ref{fig:system_model} shows the system model of the proposed framework.
Each mruby application bytecode transferred from the host to the target device is received by the loader in the RiteVM.
The RiteVM reads the transferred bytecode and executes it with libraries (Section \ref{sec:Bluetooth loader for mruby bytecode}).
The mruby applications run simultaneously due to synchronized processing.
The RiteVM scheduler switches RiteVM tasks, and multiple tasks can run concurrently (Section \ref{sec:RiteVM Scheduler}).
mruby applications are synchronized by the Eventflag (Section \ref{sec:Synchronization of Multiple RiteVM Tasks}).
In this paper, TOPPERS/HRP2 \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/system_model.eps}
    \vspace{-3mm}
\caption{System model of the proposed framework}
    \vspace{-3mm}
\label{fig:system_model}
\end{figure}

\section{Design and Implementation}
\label{sec:Design and Implementation}
% The following subsection explains these functionalities.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/component_bluetooth.eps}
    \vspace{-3mm}
\caption{Component diagram of RiteVM with Bluetooth loader}
    \vspace{-3mm}
\label{fig:component_bluetooth}
\end{figure}

\subsection{Bluetooth Loader for mruby Bytecode}
\label{sec:Bluetooth loader for mruby bytecode}
This section describes the proposed additional functionality of mruby on TECS, i.e., the Bluetooth loader.\footnote{
The Bluetooth loader is intended to improve development efficiency; therefore, software developers should use it during the development phase.
Note that the complete software should be compiled and linked on the storage/ROM device beforehand.
}
In the current system, the platform including mruby bytecodes is saved on a storage/ROM device.
Developers must rewrite the storage/ROM device every time the programs are modified.
In addition, the RTOS on the target device needs to be restarted.
The repetition hinders development efficiency.
The Bluetooth loader for mruby bytecode decreases developer burden because developers only have to connect the storage/ROM device and start the RTOS once.

@@

In the proposed framework, a platform that includes RiteVMs and an mruby library is first compiled and copied to the storage/ROM device.
On the host, the mruby application programs (.rb files) are edited and compiled to bytecodes (.mrb files) by an mruby compiler.
The generated bytecodes are transferred from the host to the target device via Bluetooth.
% This saves time since Bluetooth pairing can be avoided because the loader can load the bytecode continuously.

\subsubsection{RiteVM Component with Bluetooth Loader for mruby Bytecode}
The proposed framework provides a RiteVM with a Bluetooth loader for mruby bytecode as a TECS component.
This component is an extension of the RiteVM component described in \cite{par:mrubyonTECS}.
It receives bytecodes via Bluetooth and manages the RiteVM configuration, such as generating mruby library bytecodes automatically.
This generated bytecode is prepared beforehand on the storage/ROM device and differs from the bytecode transferred with Bluetooth.
